Debugging by \textit{lastChange}

### 2010-10-21 trunk/papers/pldi2011/sigplanconf-template.tex

%---------------------------------------------------------------------------------------------------
\section{JavaScript implementation}
The JavaScript prototype is implemented as an extension to Firebug\cite{Firebug} javasrcipt debugger. In this section, first we explain technical details for the \textit{lastChange} implementation skipped in the previous section. Then we address other issues, such as re-execution, data collection and presentation.

\subsection{Algorithm technical details}
\subsubsection{\texttt{objectId()}}
The object id is kept as a property of the object, \texttt{\_objectid}, which is not enumerable. Therefore, it will not appear in \texttt{for(property in object)} loops and has no effect on the executing program. Once \texttt{objectId()} is called on an object and the object has not \texttt{\_objectId} property, this property is defined by calling \texttt{defineProperty} JavaScript function. As a parameter it can be specified that the defined property is not enumerable. Then it is enough to assign a new generated id to this property.

\subsubsection{\texttt{scopeId()}}
The scope id is kept as a variable in the scope, \texttt{\_scopeId}. As we said, a hook is set on the first instruction of the function defines the variable. Whenever this hook hits,  \texttt{\_scopeId} variable is set by \texttt{eval()} function. For example evaluating \texttt{var \_scopeId = 50} will create a variable with name \texttt{\_scopeId} and value \texttt{50} in the local scope.

>>>>

%---------------------------------------------------------------------------------------------------
\section{JavaScript implementation}
We implemented \textit{Querypointer}, an Extension to Firebug JavaScript debugger, which provides \textit{lastChange} functionality. Firebug is an add-on of Firefox browser. Firefox JavaScript engine provides a JavaScript debugging interface and \textit{Querypointer} is developed over this interface. The debugging support in JavaScript comparing to more traditional languages such as Java and C\# is less evolved. Some part of this flaw is due to the dynamic nature of JavaScript. For example, JavaScript does not have classes and therefore setting watchpoint on properties before program execution is not possible. We explain how we could overcome these limitations and provide required operations for \textit{lastChange} algorithm implementation. Moreover, we breifly describe mechanisms for automated execution reproduction, data collection and presentation.

\subsection{Algorithm technical details}
\subsubsection{\texttt{objectId()} operation}
\texttt{objectId()} operation receives a regular JavaScript object and returns an id which is unique during one execution. This operation keeps the object id in an object property with name \texttt{\_objectId}. Once this operation receives an object, it returns \texttt{\_objectId} value if this property is already defined, otherwise it generates a new id and sets this property object. To set the property, it calls \texttt{defineProperty} standard JavaScript function. \texttt{defineProperty} receives an argument which specifies whether the property is enumerable or not. By setting the enumerable field \texttt{false} for \texttt{\_objectId}, this property will not apear in \texttt{for(property in object)} loops and therfore has no effect on the program execution. Consider that \texttt{\_objectId} is not set for all objects but only those objects that need an id.

\subsubsection{\texttt{scopeId()} operation}
The scope id is kept as a variable with name \texttt{\_scopeId} in the scope. We explained that we set a hook at the first instruction of the function which defines the variable. Once this hook hits, \texttt{\_scopeId} is set by calling \texttt{eval()} function. For example, executing \texttt{eval( var \_scopeId = 10)} creates a variable with name \texttt{\_scopeId} and value \texttt{10} in the local scope which is our interesting scope.
